### 2015-05-25 writing/SNLI paper/intro.tex
A few tweaks to the draft

NLI has been addressed using a wide variety of techniques, including
those grounded in syntactic structures, knowledge bases, and symbolic
logic. In recent years, it has become an important testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, but it is less clear that they can be
trained to support the full range of logical inferences required for
NLI. In the SemEval 2014 task aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.

>>>>

NLI has been addressed using a wide variety of techniques, including
those grounded in syntactic structures, knowledge bases, and symbolic
logic. In recent years, it has become an important testing ground for
approaches employing \emph{distributed} word and phrase
representations. Distributed representations excel at capturing
relations based in similarity, and they have proven effective at
modeling simple dimensions of meaning like evaluative sentiment
\cite{socher2013acl1}, but it is less clear that they can be
trained to support the full range of logical inferences required for
NLI. In the SemEval 2014 task aimed at evaluating distributed
representations for NLI, the best-performing systems relied heavily on
additional features and reasoning capabilities
\cite{marelli2014semeval}.
